---
title: "Export to Topic Flow Viz"
author: "Vignette Author"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Export to Topic Flow Viz}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r Create LDA Models}
library(topicflow)
year <- "2008"

#fd.path <- paste0("~/Desktop/full_disclosure_corpus/",year,".parsed")
fd.path <- paste0("~/Desktop/bugtraq_corpus/",year,".parsed")

folder <- loadFiles(fd.path)
```

```{r Create Models}
set.seed(1234)
models <- list()
models[["Jan"]] <- rawToLDA(folder,10,"Jan")
models[["Feb"]] <- rawToLDA(folder,10,"Feb")
models[["Mar"]] <- rawToLDA(folder,10,"Mar")
models[["Apr"]] <- rawToLDA(folder,10,"Apr")
models[["May"]] <- rawToLDA(folder,10,"May")
models[["Jun"]] <- rawToLDA(folder,10,"Jun")
models[["Jul"]] <- rawToLDA(folder,10,"Jul")
models[["Aug"]] <- rawToLDA(folder,10,"Aug")
models[["Sep"]] <- rawToLDA(folder,10,"Sep")
models[["Oct"]] <- rawToLDA(folder,10,"Oct")
models[["Nov"]] <- rawToLDA(folder,10,"Nov")
models[["Dec"]] <- rawToLDA(folder,10,"Dec")
```


```{r}
exportDocumentTermMatrix(models,"~/Desktop/bugtraq_topicflowviz/dtm")
exportTopicTermMatrix(models,"~/Desktop/bugtraq_topicflowviz/ttm")
```

```{r}
topic.flow <- CalculateTopicFlow(models)
write.csv(topic.flow,"~/Desktop/bugtraq_topicflowviz/topic_flow.csv")
```

Use the generated files, the original corpus (e.g. 2008.parsed), the metadata of the corpus (e.g. 2008.csv) also generated by the crawler, and the setup extension of interest (`.reply.body.txt`) as input to topicflowviz like so:

`python3 run.py -a bugtraq_2008_reply_body ~/Desktop/bugtraq_corpus/2008.parsed ~/Desktop/bugtraq_corpus/2008.csv .reply.body.txt ~/Desktop/bugtraq_topicflowviz/dtm ~/Desktop/bugtraq_topicflowviz/ttm ~/Desktop/bugtraq_topicflowviz/topic_flow.csv`

Note underlines will always turned into spaces, so when adding or deleting you can just use underlines and no double quotes on any parameter. 

